### 2013-06-05 drafts/general_writeup/writeup.tex
Added to first section of writeup.

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath} 
\usepackage{algpseudocode}
\usepackage{ amssymb }
\usepackage{listings}
\usepackage{syntax}

@@

\DeclareMathOperator*{\argmax}{arg\,max}

@@

\newcommand{\learner}{\emph{Learner }}
\newcommand{\evaluator}{\emph{Evaluator }}
\section{The problem}
In all but the simplest problems, problem solving agents suffer from vast
search spaces. Much of the research in AI, machine learning, and optimization
focuses on how to overcome this search problem. Local information can help find
better nearby solutions but make few gaurantees about global optima. Heuristic
search techniques make use of the structure of the search space and information
about the utility of partial solutions to hopefully minimize the numeber of
candidate solutions that need to be explored. Other frameworks attempt to
approximate the target search space with a more tractable, convex, surrogate
search space.

@@

Types:

\begin{grammar}
<$t$> ::= $\tau$, $\sigma$  (type variables)
  \alt $a$, $b$ (concrete types e.g. real, bool, int, etc.)
  \alt $\funtype{t'}{t}$ (function type)
\end{grammar}

Expressions: 
\begin{grammar}
<$\typedexp{e}{t}$> ::= $\typedexp{c}{t'}$ s.t. $t' = mgu(t,
\type{c})$ (substitute a terminal tree that unifies with the requesting type)
  \alt ($\typedexp{e}{\funtype{t'}{t}} \;\;\; \typedexp{e}{t'}$)
\end{grammar}

@@

As has long been noted by
Genetic Programming researchers, any solution space can be modeled as a set of
programs that generate space. As an example, if the solution space to a problem
is the set of all boolean circuits constructed from some set of gates, then the
corresponding space of programs is the set of programs that wire up boolean
circuits from those gates.

How does this realization help us? It means that if we can formulate a single
model that places a distribution over solution distributions by describing a
distribution over program generating processes.

We will first describe a simplified version of the hierarchical model over programs that we will be using. We start with a base grammar $\mathcal{G}$ of the form 
\section{The model}
The elements of any solution space can be represented as programs. u
 \section{History and related literature}
Angluin 1988~\cite{angluin1988queries}: investigates the complexity of
learning concepts that are subsets of a hypothesis space via a number
of primitive queries such as membership, equivalence, subset, etc. \\

>>>>

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath} 
\usepackage{algpseudocode}
\usepackage{ amssymb }
\usepackage{listings}
\usepackage{syntax}
\usepackage{mdframed}

@@

@@

\newcommand{\learner}{\emph{Learner }}
\newcommand{\evaluator}{\emph{Evaluator }}
\section{The problem}
In all but the simplest problems, problem solving agents suffer from vast
search spaces. Much of the research in AI, machine learning, and optimization
focuses on how to overcome this search problem. Local information can help find
better nearby solutions but makes few gaurantees about global optima. Heuristic
search techniques make use of the structure of the search space and information
about the utility of partial solutions to hopefully minimize the numeber of
candidate solutions that need to be explored. Other frameworks attempt to
approximate the target search space with a more tractable, convex, surrogate
search space.

@@

@@

As has long been noted by Genetic Programming researchers, any solution space
can be modeled as a set of programs. As an example, if the solution space to a
problem is the set of all boolean circuits constructed from some set of gates,
then the orresponding space of programs is the set of programs that wire up
boolean circuits from those gates.

How does this realization help us? It means that we can formulate a single
model that places a distribution over solution distributions by describing a
distribution over program generating processes.

We will first describe a simplified version of the hierarchical model over
programs that we will be using. We start with a base grammar $\mathcal{G}$ of
the form shown in Figure~\ref{fig:grammar}.

\begin{figure}
  \begin{grammar}
    <$e$> ::= $p_1$ | $p_2$ | \dots | $p_N$   \text{ (primitive combinators)}
              \alt (e e) \text{ (application) }
  \end{grammar}
 \caption{A grammar for a typed combinatory programming language.\label{fig:grammar}}
\end{figure}

Our probabilistic model is motivated by the fact that while $\mathcal{G}$
represents the language in which solutions are written, in any particular
domain there is a distribution $\mathcal{H}$ over solutions that is itself drawn
according to an adaptor grammar~\cite{} based on $\mathcal{G}$ and some
parameters $\theta$.

 \section{History and related literature}
Angluin 1988~\cite{angluin1988queries}: investigates the complexity of
learning concepts that are subsets of a hypothesis space via a number
of primitive queries such as membership, equivalence, subset, etc. \\
